\cvsection{Experience}

\begin{cventries}
	\cventry
	{Freelance Data Engineer}
	{Betclic (Extia) }
	{Bordeaux, France}
	{September 2024 - March 2025}
	{
		\begin{cvitems}
			\item {Migration of all Big Data pipelines from dbt Cloud to dbt Core + Airflow.}
			\item {Maintenance of pipelines for multiple internal datamarts (player data, transaction data, game activities).}
			\item {Development of new algorithms for fraud and money laundering detection.}
			\item {Improvements to CICD pipeline to decrease build times.}
			\item {dbt + Amazon Web Services / Snowflake Stack.}
		\end{cvitems}
	}
	
	\cventry
	{Freelance Data Engineer}
	{Sanofi (Eviden)}
	{Pessac, France}
	{September 2023 - September 2024}
	{
		\begin{cvitems}
			\item {Maintenance of the batch genealogy data product, in Spark Scala and GraphQL.}
			\item {Migration of pipelines and datalake to dbt and Snowflake.}
			\item {Migration of DevOps pipelines to GitHub Actions.}
			\item {Training and KT for newly recruited daa engineers.}
			\item {Amazon Web Services (Glue, Scala) / Snowflake (dbt, SQL) Stack.}
		\end{cvitems}
	}

	\cventry
	{Lead Data Engineer}
	{DataFret}
	{Bordeaux, France}
	{April 2023 - September 2023}
	{
		\begin{cvitems}
			\item {Migration of the DataFret SAS application from a local to a cloud version.}
			\item {Development of new features and implementation of the cloud architecture.}
		\end{cvitems}
	}
	
	\cventry
	{Tech Lead Data Engineer Consultant}
	{Volvo Trucks (Thélio)}
	{Bègles, France}
	{August 2022 - March 2023}
	{
		\begin{cvitems}
			\item {Databricks Lead for two teams of data engineers and data analysts, for a KPI reporting project.}
			\item {Monitoring and technical incident management, team support and knowledge sharing sessions.}
			\item {Implemented a new architecture resolve existing pain points and improve the team's work environment.}
			\item {International environment, communication in English.}
			\item {Microsoft Azure Stack (Databricks, Python).}
		\end{cvitems}
	}
	
	\cventry
	{Data Engineer Consultant}{}{}
	{February 2022 - July 2022}
	{
		\begin{cvitems}
			\item {Development of an ETL pipeline and a REST API to supply predictive maintenance data to a dashboard for Volvo Trucks customers.}
			\item {More than 10x improvement in the performance of the existing API after reimplementation of the data architecture.}
			\item {International environment, communication in English.}
			\item {Microsoft Azure Stack (Databricks, Python).}
		\end{cvitems}
	}
	
	\cventry
	{Data Engineer Consultant}
	{La Banque Postale (Thélio)}
	{Bègles, France}
	{April 2021 - January 2022}
	{
		\begin{cvitems}
			\item {Integration in the data squad, with handling of a multitude of different tasks, from maintenance to the creation of new ETL pipelines.}
			\item {Development of a parser/decoder for a internal LBP data file format.}
			\item {Cloudera on-premise Stack (Python, SQL).}
		\end{cvitems}
	}
	
	\newpage

	\cventry
	{Data Engineer Consultant}
	{Valemo (Thélio)}
	{Bègles, France}
	{February 2021 - April 2021}
	{
		\begin{cvitems}
			\item {Development of multiple ETL pipelines with Databricks.}
			\item {Microsoft Azure Stack (Databricks, Scala).}
		\end{cvitems}
	}
	
	\cventry
	{Data Engineer Consultant}
	{CDiscount Advertising (Thélio)}
	{Bègles, France}
	{February 2021 - March 2021}
	{
		\begin{cvitems}
			\item {Parsing and cleaning of marketing data for storage in BigQuery.}
			\item {Supplier API scraping for daily updates in BigQuery.}
			\item {Google Cloud Platform Stack (Dataproc, Python) with real-time data.}
		\end{cvitems}
	}
	
	\cventry
	{Research Engineer}
	{LaBRI, University of Bordeaux}
	{Talence, France}
	{October 2018 - February 2021}
	{
		\begin{cvitems}
			\item {Management of a Big Data and Machine Learning research projects.}
			\item {Development of a data pipeline to collect data from temperature and presence sensors within the university.}
			\item {Development of a neural network for research into time series prediction.}
			\item {HortonWorks/Cloudera on-premise Stack.}
		\end{cvitems}
	}
	
\end{cventries}